Reduced growth due to belowground sink limitation is not explained by reduced photosynthesis

### 2016-05-20 manuscript/manuscript_pve.Rmd
added thesis reviewer comment on future experiment only to thesis rmd

```{r install packages, echo=FALSE, message=FALSE, warning=FALSE,results="hide"}
#install packages if not already installed
.packages = c("RColorBrewer", "doBy", "sciplot", "plyr","nlme", "multcomp", "plantecophys", "scales","smatr",
                           "lme4", "lmerTest", "broom", "reporttools", "visreg", "pixiedust")

>>>>

```{r install packages, echo=FALSE, message=FALSE, warning=FALSE,results="hide"}
#install packages if not already installed
.packages = c("RColorBrewer", "doBy", "sciplot", "plyr","nlme", "multcomp", "plantecophys", "scales","smatr","plotrix",
                           "lme4", "lmerTest", "broom", "reporttools", "visreg", "pixiedust", "lubridate", "reshape",
              "magicaxis", "effects")
